Hydrodynamics and rheology of weakly adhesive vesicle doublets

### 2019-02-01 vesicle_code/docs/adhesion/adhesion.tex
working on extensional example

In Figures~\ref{fig:extensional1}--\ref{fig:extensional3}, snapshots of
a fluid trap containing a vesicle doublet of reduced area 0.7 are
simulated at different extensional rates.  While this double remains
trapped at around the stagnation point, a doublet with a reduced area of
0.8 is broken for a sufficiently large extensional rate
(Figure~\ref{fig:extensional4}).  In the left plot of
Figure~\ref{fig:extensionalPhaseDiagram}, parameter values with a blue
mark result in a fluid trap while the parameter values with a red marks
result in the vesicles separating.

For extensional rates and reduced areas that result in a fluid trap, the
initial configuration of the vesicles have the diverging stream
direction is in the parallel to the vesicles' short axis.  Since the
stable configuration of two vesicles in an extensional flow has the
converging direction parallel to the vesicles' short axis, we expect the
vesicles to align themselves with the long axis parallel to the
diverging direction.  We observe in 
Figures~\ref{fig:extensional1}--\ref{fig:extensional3} that the vesicles
do in fact undergo a rotation, but not by a complete 90 degrees.  To
further analyze this rotation, we define the inclination angle of the
doublet as described in the right plot of
Figure~\ref{fig:extensionalPhaseDiagram}.

The doublet starts at an angle of $\pi$ and rotates towards some number
less than $\pi/2$ (if it converges).

As expected, we observe two different regimes---the extensional rate is
sufficiently small that the doublet structure is not broken, and the
extensional rate is sufficiently large that the doublet is broken.  In
Figure~\ref{fig:extensionalPhaseDiagram}, the red marks correspond to
parameters where the doublet is broken while the red marks correspond to
parameters where the doublet tends to a steady-state fluid trap.  In the
case that there is a fluid trap, the doublet rotates from the unstable
configuration where the converging rate is in the direction that is
parallel to the long axis of the vesicles.  At low extensional rates,
the inclination angle approaches $\pi$ which corresponds to the
converging direction being aligned with the short axis of the vesicle
(Figure~\ref{fig:extensional1}).  As the extensional rate is increased,
the vesicle tilts to a shallower inclination angle
(Figures~\ref{fig:extensional2} and~\ref{fig:extensional3}).  Finally,
when the inclination angle is sufficiently large, the doublet is broken
(Figure~\ref{fig:extensional4}).  In
Figure~\ref{fig:extensionalPhaseDiagram}, the size of the round marks
correspond to the inclination angle.  The square marks correspond to
doublets that do not reach a steady-state inclination angle in the given
time horizon.

@@

We include a plot of the inclination angle as a function of time for
varying extensional rates (left plot of
Figure~\ref{fig:extensionalInclinationAngle}).  The inclination angle is
defined defined in with respect to the diverging direction (right plot
of Figure~\ref{fig:extensionalInclinationAngle}).  When the doublet is
broken at reduced area $0.70$, the extensional rate is sufficiently
large to align the long axis of the vesicle with the diverging direction
and then the vesicles separate.  However, for larger reduced areas, the
separation dynamics is different.  Instead, the vesicles tilt to an
inclination angle and then separate (Figure~\ref{fig:extensional4}).

@@

%Figures~\ref{fig:sflow_phase_diagram},
%~\ref{fig:sflow_1frames}, and~\ref{fig:sflow_2frames}
%\begin{figure}
%\includegraphics[keepaspectratio=true,scale=0.41]{figs/shear2Ves01a-iD12a.eps}
%\includegraphics[keepaspectratio=true,scale=0.415]{Nshear02_adS_ShearRate01.png}
%% \includegraphics[keepaspectratio=true,scale=0.40]{figs/Nshear02_adS_rA01.png}
%\caption{(a) Dynamics of a pair of vesicles in a planar shear flow with shear rate $\dot\gamma=1$ and vdW length $\delta = 0.4$. (b) Phase diagram of vesicle hydrodynamics in a shear flow. At a fixed reduced area $\triangle A=0.95$ and $\delta =0.4$,  the critical vdW potential strength $\sigma$ for binding of two vesicles in a shear flow depends on the shear rate $\dot\gamma$.}
%\label{fig:sflow_phase_diagram}
%\end{figure}

>>>>

In Figures~\ref{fig:extensional1}--\ref{fig:extensional3}, snapshots of
a fluid trap containing a vesicle doublet of reduced area 0.7 are
simulated at different extensional rates.  While this doublet remains
trapped at around the stagnation point, a doublet with a reduced area of
0.8 is broken for a sufficiently large extensional rate
(Figure~\ref{fig:extensional4}).  In the left plot of
Figure~\ref{fig:extensionalPhaseDiagram}, parameter values with a blue
mark result in a fluid trap while the parameter values with a red marks
result in the vesicles separating.  For extensional rates and reduced
areas that result in a fluid trap, the initial configuration of the
vesicles have the diverging stream direction parallel to the vesicles'
short axis.  Since the stable configuration of two vesicles in an
extensional flow has the converging direction parallel to the vesicles'
short axis, we expect the vesicles to align themselves with the long
axis parallel to the diverging direction.  We observe in
Figures~\ref{fig:extensional1}--\ref{fig:extensional3} that the vesicles
do in fact rotate, but fall short of aligning their long axis with the
diverging direction.  In the left plot of
Figure~\ref{fig:extensionalPhaseDiagram}, the size of the round dots are
scaled the final inclination angle as defined in the right plot.  At
smaller extensional rates, the vesicles comes closer to aligning their
long axis with the diverging direction.  The inclination angle is
defined defined in with respect to the diverging direction (right plot
of Figure~\ref{fig:extensionalInclinationAngle}).  When the doublet is
broken at reduced area $0.70$, the extensional rate is sufficiently
large to align the long axis of the vesicle with the diverging direction
and then the vesicles separate.  However, for larger reduced areas, the
separation dynamics is different.  Instead, the vesicles tilt to an
inclination angle and then separate (Figure~\ref{fig:extensional4}).

%As expected, we observe two different regimes---the extensional rate is
%sufficiently small that the doublet structure is not broken, and the
%extensional rate is sufficiently large that the doublet is broken.  In
%Figure~\ref{fig:extensionalPhaseDiagram}, the red marks correspond to
%parameters where the doublet is broken while the red marks correspond to
%parameters where the doublet tends to a steady-state fluid trap.  In the
%case that there is a fluid trap, the doublet rotates from the unstable
%configuration where the converging rate is in the direction that is
%parallel to the long axis of the vesicles.  At low extensional rates,
%the inclination angle approaches $\pi$ which corresponds to the
%converging direction being aligned with the short axis of the vesicle
%(Figure~\ref{fig:extensional1}).  As the extensional rate is increased,
%the vesicle tilts to a shallower inclination angle
%(Figures~\ref{fig:extensional2} and~\ref{fig:extensional3}).  Finally,
%when the inclination angle is sufficiently large, the doublet is broken
%(Figure~\ref{fig:extensional4}).  In
%Figure~\ref{fig:extensionalPhaseDiagram}, the size of the round marks
%correspond to the inclination angle.  The square marks correspond to
%doublets that do not reach a steady-state inclination angle in the given
%time horizon.

@@

For very low extensional rates, the time horizon is insufficient for the
doublet to reach a steady state, and these simulations are marked with a
square.  In Figure~\ref{fig:extensionalInclinationAngle}, we plot the
inclination angle as a function of time for four different extensional
rates (left) and the final inclination angle for all doublets that reach
a steady state (right).  We observe that not only do larger smaller
extensional rates result in smaller inclination angles, but smaller
reduced areas also result in smaller inclination angles.

We further characterize the dynamics by examining the vorticity and
total force on the vesicles.

@@
